The Shape and Color of Politics

### 2023-10-12 chapter_2/src/slides/slides.qmd
update a new draft of slides

@@

## Integrating key perspectives from the cognitive sciences

![[@collins_spreading-activation_1975]](../../assets/slides/imgs/collins_loftus.png){.absolute top=100}
![[@fazio_attitudes_2007]](../../assets/slides/imgs/fazio.png){.absolute bottom=100}

![[@sander_cambridge_2013]](../../assets/slides/imgs/affective_neuro.jpg){.absolute top=100 height=600}
![[@adolphs_emotion_2011]](../../assets/slides/imgs/affective_neuroscience.webp){.absolute bottom=100 right=0}

![[@zajonc_feeling_1980]](../../assets/slides/imgs/zajonc.png){.absolute top=50 right=50 height=300}
![](../../assets/slides/imgs/erisen_et-al.png){.absolute bottom=50 left=50}

## Canonical models of **political** information processing

![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute left=0}
![](../../assets/slides/imgs/zaller_feldman.png){.absolute right=0}
![[@taber_motivated_2006]](../../assets/slides/imgs/taber_lodge.png){.absolute top=200 right=0}
![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute top=100}
![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute top=400}

>>>>

![[Kirkland Signature]()](../../assets/slides/imgs/kirkland.svg){#fig-kirkland width=6.5in}

![[BP]()](../../assets/slides/imgs/bp.png){#fig-bp width=6.5in}

![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}

@@
